Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-04-15 ref_response/ProjectNarrative.tex
small tweaks
minor wording

\pagestyle{fancy}
\fancyhf{}
\lhead{\fancyplain{}{\doctitle}}
\rhead{\fancyplain{}{M.A. Pajkos}}
\rfoot{\fancyplain{}{\thepage}}

@@

\setcounter{page}{1} \pagenumbering{arabic} \renewcommand{\thepage}
           {Ref Report-- \arabic{page}}%\pagestyle{plain}

\begin{center}
{\bf Referee Report} \vspace{-0.2in}
%\section*{Project Narrative}
\end{center}

Referee Report

@@

\textbf{Edits made in the paper are colored in red and begin with the number corresponding to the referee's specific comment.  The referee's comments are insightful and help add nuance to our project.  Below we outline the changes made with respect to each comment.}\\

@@

>>>>

\pagestyle{fancy}
\fancyhf{}
\lhead{\fancyplain{}{PUT THE AAS JOURNALS MANUSCRIPT NUM HERE}}
\rhead{\fancyplain{}{M.A. Pajkos et al.}}
\rfoot{\fancyplain{}{\thepage}}

@@

\setcounter{page}{1} \pagenumbering{arabic} \renewcommand{\thepage}
           {\arabic{page}}%\pagestyle{plain}

\begin{center}
{\bf Response to Referee} \vspace{-0.2in}
%\section*{Project Narrative}
\end{center}

Referee's comments in this font

@@

\textbf{We thank the referee for a thorough and constructive review of our manuscript. In updated draft, we have addressed each of the points raised by the referee and, below, we give our reply to each issue in turn. We also described all changes we have made to the manuscript.
Edits made in the manuscript are colored in red and begin with the number corresponding to the referee's specific comment.  The referee's comments are insightful and help add nuance to our project.  Below we outline the changes made with respect to each comment.}\\

@@

\textbf{We re-worded a strong statement regarding the SASI and its importance for explosions in Section 3.4.}
